Scattering from compact objects: \\ Regge poles and the Complex Angular Momentum method

### 2019-12-21 rainbowCAM.tex
Minor changes to Appendix A, and the text in the main body that refers to this.y

After scanning across the domain, we find no evidence of Regge poles in the fourth quadrant of the complex-$\lambda$ plane for $\omega>0$. Exploring the second and third quadrants, where $\text{Re}[{\lambda}] < 0$, requires a choice to be made on the form of the boundary condition imposed at $r=0$. A natural choice is to impose regularity, i.e.,~$\phi_{\omega\ell} \sim r^{-\lambda+1/2}$ as $r \rightarrow 0$ for $\text{Re} [\lambda] < 0$. An advantage of this choice is that it leads to the same symmetry as in the black hole case for the $S$-matrix elements (see Ref.~\cite{Andersson:1994rk,Folacci:2019cmc}), viz.,
\begin{equation}\label{Matrix_S_CAM_symm}
S_{-\lambda -1/2}(\omega) =  e^{-2i \pi \lambda} \, S_{\lambda -1/2}(\omega)
\end{equation}

@@

\moh{I have established some proprieties (symmetry relations) to connect different quadrants and I moved part of the paragraph from section III-c to the appendix.  Sam \& Tom : Please be critical and It is free to change.}
\tom{I have made a few minor rewordings. Agree with moving III C para to here.}.

In this appendix, we will show that, for $\omega$ real, the zeros of the $S$-matrix (\textit{i.e.}, the Regge poles), or in other words
the zeros of the coefficient $A^{(-)}_{\lambda-1/2} (\omega)$ [see Eq.~\eqref{Matrix_S_CAM}]
\begin{equation}\label{zeros_Am}
   A^{(-)}_{\lambda-1/2} (\omega)\Big{|}_{\lambda =\lambda_n} = 0
\end{equation}
are lying in the right-half of the complex $\lambda$-plan.

\tom{ rewording: In this appendix we will show which quadrants of the complex $\lambda$-plane may contain the Regge poles for scalar and axial metric perturbations on a stellar background. In other words, we will constrain the possible locations of the zeros of the coefficient $A^{(-)}_{\lambda-1/2} (\omega)$ [see Eq.~\eqref{Matrix_S_CAM}],
\begin{equation}\label{zeros_Am}
   A^{(-)}_{\lambda-1/2} (\omega)\Big{|}_{\lambda =\lambda_n} = 0,
\end{equation}
for $\omega$ real.
}

To do this, it is convenient to write the boundary conditions \eqref{bc_1_in} and \eqref{bc_2_in} in the following form:
\begin{equation}
\label{bc_CAM}
\phi_{\lambda-\frac{1}{2}}(\omega) \sim
\left\{
\begin{aligned}
&r^{\lambda+\frac{1}{2}}\hspace{8em} \scriptstyle{r \rightarrow 0,} \quad \text{(regular solution)}\\
&A_{\lambda-1/2}^{(-)}(\omega) e^{-i\omega r_*} + A_{\lambda-1/2}^{(+)}(\omega) e^{+i\omega r_*}  \hspace{0.2em}\scriptstyle{r_* \rightarrow +\infty.}
\end{aligned}
\right.
\end{equation}

Let us consider the radial equation~\eqref{H_Radial_equation}, written for the regular solution
\begin{equation}\label{Wave_equation_reg}
   \frac{d^2}{dr_*^2}\phi_{\omega,\lambda-1/2}(r)+\left(\omega^2 -V_{\lambda-1/2}\right) \phi_{\omega,\lambda-1/2}(r) =0
 \end{equation}
and its complex conjugate
 \begin{equation}\label{Wave_equation_reg_conjugate}
   \frac{d^2}{dr_*^2}\phi^*_{\omega,\lambda-1/2}(r)+ \left(\omega^2 -V_{\lambda^*-1/2}\right)\phi^*_{\omega,{\lambda-1/2}}(r) =0
 \end{equation}
Multiplying \eqref{Wave_equation_reg} by $\phi^*_{\omega,\lambda-1/2}(r)$ and \eqref{Wave_equation_reg_conjugate} by $\phi_{\omega,\lambda-1/2}(r)$ and subtracting, it follows that
\begin{widetext}
\begin{equation}\label{Derivative_Wronskian}
\begin{aligned}
 \phi^*_{\omega,\lambda-1/2}(r) \frac{d^2}{dr_*^2}\phi_{\omega,\lambda-1/2}(r) - \phi_{\omega,\lambda-1/2}(r) \frac{d^2}{dr_*^2} \phi^*_{\omega,\lambda-1/2}(r) &= 2 i|\phi_{\lambda-1/2}(\omega)|^2 f[r]\frac{2\text{Re}[\lambda]\text{Im}[\lambda]}{r^2} \\
                           &= 2 i|\phi_{\lambda-1/2}(\omega)|^2 f[r]\frac{\text{Im}[\lambda^2]}{r^2}
 \end{aligned}
\end{equation}
\end{widetext}
The LHS of Eq.~\eqref{Derivative_Wronskian} is the derivative of the Wronskian, $W$, of the two solutions with respect to $r_*$ and it is a constant (\textit{i.e.}, $d/dr_* W[\phi^*,\phi] = 0$) if $\lambda$ either real or purely imaginary. According to Eq.~\eqref{Derivative_Wronskian}, we can write
\begin{equation}\label{Derivative_Wronskian_bis}
\frac{d}{dr_*}W[\phi^*,\phi]= 2i|\phi_{\lambda-1/2}(\omega)|^2 f[r]\frac{2\text{Re}[\lambda]\text{Im}[\lambda]}{r^2}.
\end{equation}

Integration of \eqref{Derivative_Wronskian_bis} gives
\begin{equation}\label{Evaluation_W}
\lim_{r_*\rightarrow \infty}  W[\phi^*,\phi] = 4i\, \text{Im}[\lambda]\, \text{Re}[\lambda] \int_{0}^{+\infty} \frac{|\phi_{\lambda-1/2}(\omega)|^2}{r^2}\,dr
\end{equation}
where we have used $\frac{dr}{dr_*}=f(r)$ to transform the integration variable. On the other hand,  by evaluating the  Wronskian from the boundary condition~\eqref{bc_CAM}, we obtain
\begin{equation}\label{Evaluation_W_bis}
\lim_{r_*\rightarrow \infty}  W[\phi^*,\phi] =-2i\, \omega\left(|A^{(-)}_{\lambda-1/2}|^2-|A^{(+)}_{\lambda-1/2}|^2\right),
\end{equation}
hence we get (\textit{c.f.} \eqref{Evaluation_W} and  \eqref{Evaluation_W_bis})
\begin{equation}\label{Evaluation_W_bis_1}
  |A^{(-)}_{\lambda-1/2}|^2-|A^{(+)}_{\lambda-1/2}|^2 = -\frac{2}{\omega}\text{Re}[\lambda]\text{Im}[\lambda]\int_{0}^{+\infty} \frac{ |\phi_{\lambda-1/2}(\omega)|^2}{r^2}\,dr.
\end{equation}

@@

The results established here agree with the situation in non-relativistic wave and atom/particle scattering (see \textit{e.g.} \cite{Newton:1982qc,Bottino1962} and references therein), also with the Schwarzschild black hole scattering \cite{Andersson:1994rk,Decanini:2009mu}.

>>>>

In Appendix \ref{appen} we present an argument for why no Regge poles are expected to be located in the fourth quadrant of the complex-$\lambda$ plane for $\omega>0$. As a consistency check, 
we have scanned the fourth quadrant with the numerical method above, and have found no evidence for Regge poles.

Exploring the second and third quadrants, where $\text{Re}[{\lambda}] < 0$, requires a choice to be made on the form of the boundary condition imposed at $r=0$. A natural choice is to impose regularity, i.e.,~$\phi_{\omega\ell} \sim r^{-\lambda+1/2}$ as $r \rightarrow 0$ for $\text{Re} [\lambda] < 0$. An advantage of this choice is that it leads to the same symmetry as in the black hole case for the $S$-matrix elements (see Ref.~\cite{Andersson:1994rk,Folacci:2019cmc}), viz.,
\begin{equation}\label{Matrix_S_CAM_symm}
S_{-\lambda -1/2}(\omega) =  e^{-2i \pi \lambda} \, S_{\lambda -1/2}(\omega)
\end{equation}

@@

%\moh{I have established some proprieties (symmetry relations) to connect different quadrants and I moved part of the paragraph from section III-c to the appendix.  Sam \& Tom : Please be critical and It is free to change.}
%\tom{I have made a few minor rewordings. Agree with moving III C para to here.}.

%In this appendix, we will show that, for $\omega$ real, the zeros of the $S$-matrix (\textit{i.e.}, the Regge poles), or in other words
%the zeros of the coefficient $A^{(-)}_{\lambda-1/2} (\omega)$ [see Eq.~\eqref{Matrix_S_CAM}]
%\begin{equation}\label{zeros_Am}
%   A^{(-)}_{\lambda-1/2} (\omega)\Big{|}_{\lambda =\lambda_n} = 0
%\end{equation}
%are lying in the right-half of the complex $\lambda$-plan.

In this appendix, we establish which quadrants of the complex $\lambda$-plane may contain Regge poles, for scalar and axial metric perturbations on a stellar background. In other words, we will constrain the possible locations of the zeros of the coefficient $A^{(-)}_{\lambda-1/2} (\omega)$ [see Eq.~\eqref{Matrix_S_CAM}],
\begin{equation}\label{zeros_Am}
   A^{(-)}_{\lambda-1/2} (\omega)\Big{|}_{\lambda =\lambda_n} = 0,
\end{equation}
for $\omega$ real.

To do this, it is convenient to write the boundary conditions \eqref{bc_1_in} and \eqref{bc_2_in} defining a solution that is regular at the origin in the following form:
\begin{equation}
\label{bc_CAM}
\phi_{\lambda-\frac{1}{2}}(\omega) \sim
\begin{cases}
r^{\lambda+\frac{1}{2}}, &
r \rightarrow 0, \\
\phantom{+} A_{\lambda-1/2}^{(-)}(\omega) e^{-i\omega r_*} & \\ 
 + A_{\lambda-1/2}^{(+)}(\omega) e^{+i\omega r_*} , &r_* \rightarrow +\infty.
\end{cases}
\end{equation}
%
We next consider the radial equation~\eqref{H_Radial_equation} for the regular solution
\begin{equation}\label{Wave_equation_reg}
   \frac{d^2}{dr_*^2}\phi_{\omega,\lambda-1/2}(r)+\left(\omega^2 -V_{\lambda-1/2}\right) \phi_{\omega,\lambda-1/2}(r) =0,
 \end{equation}
and its complex conjugate, 
 \begin{equation}\label{Wave_equation_reg_conjugate}
   \frac{d^2}{dr_*^2}\phi^*_{\omega,\lambda-1/2}(r)+ \left(\omega^2 -V_{\lambda^*-1/2}\right)\phi^*_{\omega,{\lambda-1/2}}(r) = 0 .
 \end{equation}
Multiplying \eqref{Wave_equation_reg} by $\phi^*_{\omega,\lambda-1/2}(r)$ and \eqref{Wave_equation_reg_conjugate} by $\phi_{\omega,\lambda-1/2}(r)$ and taking the difference, it follows that
\begin{widetext}
\begin{equation}\label{Derivative_Wronskian}
\begin{aligned}
 \phi^*_{\omega,\lambda-1/2}(r) \frac{d^2}{dr_*^2}\phi_{\omega,\lambda-1/2}(r) - \phi_{\omega,\lambda-1/2}(r) \frac{d^2}{dr_*^2} \phi^*_{\omega,\lambda-1/2}(r) %&= 2 i|\phi_{\lambda-1/2}(\omega)|^2 f[r]\frac{2\text{Re}[\lambda]\text{Im}[\lambda]}{r^2} \\
                           &= 2 i|\phi_{\lambda-1/2}(\omega)|^2 f[r]\frac{\text{Im}[\lambda^2]}{r^2} .
 \end{aligned}
\end{equation}
\end{widetext}
The LHS of Eq.~\eqref{Derivative_Wronskian} is the derivative of $W$, the Wronskian of the two solutions with respect to $r_*$. The Wronskian is a constant (\textit{i.e.}, $d/dr_* W[\phi^*,\phi] = 0$) if $\lambda$ either real or purely imaginary. According to Eq.~\eqref{Derivative_Wronskian}, we can write
\begin{equation}\label{Derivative_Wronskian_bis}
\frac{d}{dr_*}W[\phi^*,\phi]= 2i|\phi_{\lambda-1/2}(\omega)|^2 f[r]\frac{2\text{Re}[\lambda]\text{Im}[\lambda]}{r^2}.
\end{equation}

Integration of \eqref{Derivative_Wronskian_bis} gives
\begin{equation}\label{Evaluation_W}
\lim_{r_*\rightarrow \infty}  W[\phi^*,\phi] = 4i\, \text{Im}[\lambda]\, \text{Re}[\lambda] \int_{0}^{+\infty} \frac{|\phi_{\lambda-1/2}(\omega)|^2}{r^2}\,dr ,
\end{equation}
where we have used $\frac{dr}{dr_*}=f(r)$ to transform the integration variable. On the other hand,  by evaluating the  Wronskian from the boundary condition~\eqref{bc_CAM}, we obtain
\begin{equation}\label{Evaluation_W_bis}
\lim_{r_*\rightarrow \infty}  W[\phi^*,\phi] =-2i\, \omega\left(|A^{(-)}_{\lambda-1/2}|^2-|A^{(+)}_{\lambda-1/2}|^2\right),
\end{equation}
hence we get (\textit{c.f.}~\eqref{Evaluation_W} and  \eqref{Evaluation_W_bis})
\begin{equation}\label{Evaluation_W_bis_1}
  |A^{(-)}_{\lambda-1/2}|^2-|A^{(+)}_{\lambda-1/2}|^2 = -\frac{2}{\omega}\text{Re}[\lambda]\text{Im}[\lambda]\int_{0}^{+\infty} \frac{ |\phi_{\lambda-1/2}(\omega)|^2}{r^2}\,dr.
\end{equation}

@@

The results established here agree with the situation in non-relativistic wave and atom/particle scattering (see \textit{e.g.}~\cite{Newton:1982qc,Bottino1962} and references therein), and also with the results of Schwarzschild black hole scattering \cite{Andersson:1994rk,Decanini:2009mu}.
